Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-06 paper.tex
minor tweaks on paper, added forward euler

% Put your stuff here
\twocolumn[
    \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
We implement the parareal algorithm to solve various ODEs and compare in terms of accuracy, speedup and efficiency.  We explore the effect of using differnt solution operators (a course and a fine as required by the method)  The majority of our code is written in python using mpi4py to parallelize.  To compare to more performance-based languages, we compare certain codes to an implementation in C++.
    \end{abstract}
  \end{@twocolumnfalse}
]
\section{Background}

@@

\subsection{Comparison to Serial with $G_{fine}$ as \\a Forward Euler with Smaller $\Delta t$}

\subsection{Comparison to Serial with $G_{fine}$ as \\Higher Order Methods}

>>>>

% Put your stuff here
\twocolumn[
    \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
    We implement the parareal algorithm to solve various ODEs and compare in
    terms of accuracy, speedup and efficiency. We explore the effect of using
    differnt solution operators (a coarse and a fine as required by the method)
    The majority of our code is written in python using mpi4py to parallelize.
    To compare to more performance-based languages, we compare certain codes to
    an implementation in C++.
    \end{abstract}
  \end{@twocolumnfalse}
]
\section{Background}

@@

\subsection{Comparison to Serial with $g_{fine}$ as \\a Forward Euler with
Smaller $\Delta t$}

\subsection{Comparison to Serial with $g_{fine}$ as \\Higher Order Methods}
